Fluent statistical computing interfaces for biological data analysis

### 2020-07-27 Rmd/05-embeddings.Rmd
remove media9 for preparation of screenshots.

display_vid_latex <- function(key, lookup) {
    video <- lookup[lookup$key == key, ]
    glue::glue(
    "\\begin{{center}}
   \\includemedia[
    width=0.6\\linewidth,
    height=0.45\\linewidth,
    keepaspectratio=true,
    activate=pageopen
    addresource={video},
    flashvars={{%
      source={video}
      &autoPlay=true
      &loop=true}
  ]{{}}{{VPlayer.swf}}
  \\end{{center}}",
  video = video[["path"]]
  )
}

@@

```{r gaussian, results="asis", eval = knitr::is_latex_output()}
cat(display_vid_latex("gaussian", vid_lookup))
```

@@

```{r hierachical, results='asis', eval = knitr::is_latex_output()}
cat(display_vid_latex("hierachical", vid_lookup))
```

@@

####

@@

```{r trees-01, results='asis', eval = knitr::is_latex_output()}
cat(display_vid_latex("trees-01", vid_lookup))
```

@@

```{r trees-02, results='asis', eval = knitr::is_latex_output()}
cat(display_vid_latex("trees-02", vid_lookup))
```

@@

```{r mouse-01, results='asis', eval = knitr::is_latex_output()}
cat(display_vid_latex("mouse-01", vid_lookup))
```

@@

```{r mouse-02, results='asis', eval = knitr::is_latex_output()}
cat(display_vid_latex("mouse-02", vid_lookup))
```

>>>>

@@

```{r gaussian, eval = knitr::is_latex_output()}
```

@@

```{r hierachical, results='asis', eval = knitr::is_latex_output()}
```

@@

#### Piecewise linear structure

@@

```{r trees-01, eval = knitr::is_latex_output()}
```

@@

```{r trees-02, eval = knitr::is_latex_output()}
```

@@

```{r mouse-01, eval = knitr::is_latex_output()}
```

@@

```{r mouse-02, eval = knitr::is_latex_output()}
```
